---
title: "README"
author: "Rasmus Kirkegaard"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: github_document
always_allow_html: true
---

## Aim

To make it easier to get an overview of the performance you can get for nanopore basecalling with [dorado](https://github.com/nanoporetech/dorado) using a specific GPU. 

## How to contribute?

* Download some 5khz pod5 data ([zenodo](https://zenodo.org/records/15180194))
* Download [dorado](https://github.com/nanoporetech/dorado)
* Run basecalling `dorado basecaller --device  'cuda:0' sup pod5/ > basecalls.bam`
* Add your samples/s output to [google form](https://forms.gle/Qw1wiL662YrbHPxk6)

## Data availability

The collected information is available in [this google sheet](https://docs.google.com/spreadsheets/d/1p_oqalXtyMomcoeh0CE-crBgxsGifBYMvTR7hHBqmEw/edit?usp=sharing) 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 10)
```

```{r  echo=FALSE,message=FALSE,results='asis'}
library(tidyverse)
library(gsheet)
d<-gsheet2tbl('https://docs.google.com/spreadsheets/d/1p_oqalXtyMomcoeh0CE-crBgxsGifBYMvTR7hHBqmEw/edit?usp=sharing')

GPU_specs<-read_csv("GPU_specs.csv")

# Arrange
architecture_year_map <- tapply(GPU_specs$`Architecture Release Year`, GPU_specs$Architecture, unique)

# Sort the unique architecture names based on their release year
sorted_architectures <- names(sort(unlist(architecture_year_map)))

# Relevel the 'Architecture' factor based on the sorted order
GPU_specs$Architecture <- factor(GPU_specs$Architecture, levels = sorted_architectures)



dw_specs<-left_join(d,GPU_specs)

dw_specs_sorted <- dw_specs[order(dw_specs$`Architecture Release Year`, dw_specs$`Gbp/day`), ]
sorted_gpus <- unique(dw_specs_sorted$`GPU`)
dw_specs$`GPU` <- factor(dw_specs$`GPU`, levels = sorted_gpus)

```

## Basecalling performance

```{r echo=FALSE,message=FALSE}
dw_specs %>% 
  ggplot(aes(y = `Gbp/day`,x = GPU,fill=Architecture))+
  geom_hline(yintercept = 50,colour = "red",linetype = "dashed")+
  geom_hline(yintercept = 100,colour = "blue",linetype = "dashed")+
  geom_bar(stat="identity")+
  facet_grid(rows=vars(Architecture),scales="free",space = "free")+
  #annotate(geom="text", x=4, y=70, label="1 PromethION flowcell",color="red")+
  coord_flip()+
  theme_bw()+
  theme(legend.position = "NONE")
```

