---
title: "README"
author: "Rasmus Kirkegaard"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: github_document
always_allow_html: true
---

## Aim

To make it easier to get an overview of the performance you can get for nanopore basecalling with [dorado](https://github.com/nanoporetech/dorado) using a specific GPU. 

## How to contribute?

* Download some 5khz pod5 data ([zenodo](https://zenodo.org/records/15180194))
* Download [dorado](https://github.com/nanoporetech/dorado)
* Run basecalling `dorado basecaller --device  'cuda:0' sup pod5/ > basecalls.bam`
* Add your samples/s output to [google form](https://forms.gle/Qw1wiL662YrbHPxk6)

## Data availability

The collected information is available in [this google sheet](https://docs.google.com/spreadsheets/d/1p_oqalXtyMomcoeh0CE-crBgxsGifBYMvTR7hHBqmEw/edit?usp=sharing) 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 10)
```

```{r  echo=FALSE,message=FALSE,results='asis'}
library(tidyverse)
library(gsheet)
library(scales)
d<-gsheet2tbl('https://docs.google.com/spreadsheets/d/1p_oqalXtyMomcoeh0CE-crBgxsGifBYMvTR7hHBqmEw/edit?usp=sharing') %>% group_by(GPU) %>% filter(`Gbp/day`==max(`Gbp/day`)) %>%  slice_head(n = 1)

GPU_specs<-read_csv("GPU_specs.csv")

# Arrange
architecture_year_map <- tapply(GPU_specs$`Architecture Release Year`, GPU_specs$Architecture, unique)

# Sort the unique architecture names based on their release year
sorted_architectures <- names(sort(unlist(architecture_year_map)))

# Relevel the 'Architecture' factor based on the sorted order
GPU_specs$Architecture <- factor(GPU_specs$Architecture, levels = sorted_architectures)



dw_specs<-left_join(d,GPU_specs)

dw_specs_sorted <- dw_specs[order(dw_specs$`Architecture Release Year`, dw_specs$`Gbp/day`), ]
sorted_gpus <- unique(dw_specs_sorted$`GPU`)
dw_specs$`GPU` <- factor(dw_specs$`GPU`, levels = sorted_gpus)

```

## Basecalling performance

The red line indicates the capacity needed to basecall 1 PromethION flowcell (yielding 150 Gbp/72hours), the blue line 2 flowcells.

```{r echo=FALSE,message=FALSE,warning=FALSE, fig.height=7}
dw_specs %>% 
  ggplot(aes(y = `Gbp/day`,x = GPU,fill=Architecture,label=`Gbp/day`))+
  geom_hline(yintercept = 50,colour = "red",linetype = "dashed")+
  geom_hline(yintercept = 100,colour = "blue",linetype = "dashed")+
  geom_bar(stat="identity")+
  geom_text(aes(y=(`Gbp/day`+4)))+
  facet_grid(rows=vars(Architecture),scales="free",space = "free")+
  #annotate(geom="text", x=4, y=70, label="1 PromethION flowcell",color="red")+
  scale_y_continuous(breaks = breaks_pretty(10))+
  coord_flip()+
  theme_bw()+
  theme(legend.position = "NONE")+theme(strip.text.y = element_text(angle = 0))
```

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>



----------------------------------------------------------------------------------------------------------------------------------------




## Do not calculate the price/performance for your GPUs!!!

For the consumer cards it is easy to get [pricing info from wikipedia](https://en.wikipedia.org/wiki/List_of_Nvidia_graphics_processing_units). However, for the data center cards it is more challenging so the numbers here will not reflect the best deals available and will vary a lot by region and whether price info is available at all. If someone has a good source for prices for data center GPUs that would be great. For now I can only recommend that you do not trust the price/perfomance calculations as "true" numbers but they might give you a hint that datacenter GPUs means you have to pay quite a bit more to get the perfomance you see from consumer grade GPUs. 

<br>
<br>

Lower values = more basecalling for your dollars.

```{r echo=FALSE,message=FALSE,warning=FALSE, fig.height=7}
dw_specs %>% filter(!is.na(`Release price or some webshop price (USD)`)) %>%
  mutate(PricePerformance=round(`Release price or some webshop price (USD)`/`Gbp/day`)) %>%
  ggplot(aes(y = PricePerformance,x = GPU,fill=Architecture,label=PricePerformance))+
  geom_bar(stat="identity")+
  #geom_text(aes(y=(PricePerformance+20)))+
  ylab("Price performance (USD/daily Gbp)")+
  facet_grid(rows=vars(Architecture),scales="free",space = "free")+
  coord_flip()+
  theme_bw()+
  theme(legend.position = "NONE")+theme(strip.text.y = element_text(angle = 0))
```

